Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-07-19 extended_catalog/paper/extended_catalog.tex
new plot

\begin{abstract}
We present a new method for analyzing spatially extended sources with
the Large Area Telescope (LAT), the primary science instrument
on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
series of Monte Carlo studies to validate this tool
and calculate the LAT's detection threshold to spatially extended
sources.  We then apply this tool to test all sources in the two
year source catalog for extension and report on the discovery
of XXXXXX\todo{What number should be put
here. Should we report the total number of extended sources instead of the
number of new sources???} new extended sources.
\end{abstract}

@@

\todo[inline]{Add note about how difficult lat analysis in
the galactic plane is because of large PSF, low statistics,
and high source density. Describe how it requires a certain amount
of iterative, by eye modifying of the sky model. Not
adequate to simply use 2FGL}

@@

Being able to spatially resolve the \gev emission from a source is
important for several reasons. Because of the large point spread
function (PSF), there are often several possible source counterparts.
Finding a matching morphology can be used to uniquely identify the source.
Because of the largely varying PSF of the LAT, the spatial and spectral
information about a source do not nicely decouple. Therefore, a biased
spatial model will bias the spectral model of the source and studyign
the extension of the source can correct for htis.  Furthermore, correctly
modeling a source's extension is important for improving the overall model
of the sky and removing excess residuals.  These residuals manifested
themselves in the one year catalog as spurious point sources in the
region region surrounding the Large Magellanic Cloud (\cite{first_cat}).

@@

\pointlike is important for LAT analysis
that require many iterations such as source localization and extension
fitting.  On the other hand, we expect that the spectral paramaters
fit by \gtlike to be slightly more precise.
Furthermore, because \gtlike is the standard likelihood analysis package,
it has been more extensively validated for spectral analysis.
For that reason, in the following analysis we took the best fit
position and extension found by \pointlike and
refit the spectral spectral parameters using \gtlike.
\gtlike also provides a second calculation of the likelihood which gives a
second measure of \ts and \tsext. We do not consider a source to be
significant unless there is agreement between the two methods.

@@

This is important when comparing morphologies to other wavelengths
because the quoted size can vary significantly depending on which quanity
is reported.  This effect can be best seen in figure~\ref{compare_r68}
which a counts map of an extended source simulated in the energy
range from 1 \gev to 100 \gev with a uniform disk spatial model and
$\sigma=05$. Overlaid on the plot is the fit extension assuming the
source has a uniform disk and a Gaussian spatial model. The plot overlays
both $\sigma$ and $\rsixeight$ and $\sigma$ is significantly larger for
the disk spatial hypothesis compared to the Gaussian spatial model. On
the other hand, the disk and Gaussian's 68\% containment radius are
similar.

@@

We simulated point sources of varying spectral models and fit them
them using \pointlike as both point and extended sources. The data was
simulated using \gtobssim\footnote{\gtobssim is distributed
by the Fermi Science Support Center (\cite{fssc}).}
The point sources were simulated with a power-law spectral model with
six $>100$ \mev fluxes ranging from $3\times 10^{-9} \ph/\cm^2/\sec$ to
$10^{-6} \ph/\cm^2/\sec$.  The point sources were simulated with spectral
indices ($\gamma$) of 1.5, 2, 2.5, and 3.  These values were picked to
to represent the types of sources detectable by the LAT.  The point
sources were simulated on top of an isotropic power-law background
with a Sreekumar-like spectrum ($>100$ \mev flux of 1.5e-5 and spectral
index 2.1) (\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
performed over a one year time interval using a default rocking profile
and a representative livetime fraction of 0.8.  The reconstruction was
performed with photons from an energy range of 1 \gev to 100 \gev using 4
energy bins per decade and using the Pass 7 Version 6 Source instrument
response function (IRFs).  For each point source, we used \pointlike
to fit it as both a point and extended source and calculate \tsext and
we only dept the sources which had a significant point source detection
($\ts>25$).

@@

\todo[inline]{Add note about how we had to delete nearby sources which
were not hard above 10 \gev for analysis to converge.}

The LAT two year catalog presented a search for all statistically
significant sources that are detected in the \gev sky (\cite{second_cat}).
The catalog group's source finding method assumes that the emission
originated as point sources and what was presented was a list of all
sources fit assuming a point source spatial hypothesis.  Published
extended sources were modeled by the catalog group as being extended,
but no attempt was made to test if other sources in the catalog could
be spatially resolved.

We performed a search of all Fermi sources found in the second Fermi LAT
catalog for extension.  To perform this search, we built a model of the
sky consistent with the two year catalog's model.   We used the same two
years of data from August 4, 2008 to August 1, 2010 and we used the same
pass 7 Version 6 Source IRFs.  We used the same galactic diffuse,
isotropic diffuse, and earth limb emission model. The spectrum of the
galactic and isotropic diffuse models were refit during the analysis
while the earth limb emission was fixed to it's predicted value.

We performed the extension fit using \pointlike.  For each source, we
used a circular $10\deg$ region of interest centered on our source and
using 4 bins uniformly in each logarithm of energy.  We included all
background catalog sources within $15\deg$ of the source of interest
and refit the spectral parameters of sources within $2\deg$ of our source.

As was shown, we gain little in sensitivity using photons with energies
below 1 \gev. On the other hand, the large PSF at low energy makes us
more susceptible to systematic errors arising from source confusion due
to multiple point sources and susceptible to incorrect modeling of the
galactic diffuse emission.  For that reason, we performed our search
using photons only between 1 \gev and 100 \gev.

We also performed a search for extended sources using photons only between
10 \gev and 100 \gev. Even though we are testing the same sources, this
approach is complimentary because there are regions in the galactic
plane where at lower energies the diffuse emission dominates and is
likely not perfectly modeled. On the other hand, at the highest energies
accessible by the LAT, the galactic diffuse emission will be smaller and
we might expect to detect significantly harder sources. This approach is
also beneficial because harder sources with nearby neighbors that are
softer may end up being incorrectly fit at lower energies but correctly
found looking only at the high energy.  This is also beneficial in the
galactic plane looking for possible extended sources near pulsars which
are bright at lower energy but cutoff before 10 \gev.  This approach
of using only photons with energy above 10 \gev was successfully used
to detecting HESS J1825-137 with the LAT (\cite{fermi_hess_j1825}).

For each catalog source, we modified the spectral index of the source
to be a power-law. We did this for two reasons. The first is that for a
source to be significantly extended, we would expect it to be reasonably
hard and therefore be fit reasonably well by a power-law.  The second reason
is that since we begin our analysis at either 1 \gev or 10 \gev, we didn't
expect there to be significant curvature over this smaller energy range.
This method has the advantage that for the following analysis, we can
simply quote the fit power-law spectral index.

Finally, when analyzing our region, we automatically removed all other
catalog sources which were within 0.5\deg. This was done because of
a concern that truly extended sources might end up in the catalog as
multiple point sources. These spurious nearby catalogs sources might then
distort our fit enough that it no longer would show up as being extended.
Nevertheless, we investigated for each of our extended candidates if
if we seemed to be legitimately removing real background sources. And
we employed a dual localization procedure (described above) to test
all of our candidates for source confusion.

For each catalog source, we modified the source to have a uniform radially
symmetric disk spatial shape and used \pointlike to simultaneously fit
the position and extension of the source.  We then selected all of the
sources for which \pointlike found $\tsext>16$.

@@

We expect most extended sources to be inside the galactic plane
since extragalactic sources are typically too far away to be
resolvable. Unfortunately, the \gev emission in the galactic plane
is dominated by anisotropic galactic diffuse emission.  Modeling the
galactic diffuse emission and finding sources on top of this emission is
difficult~\ref{first_diffuse_paper}. This issue has been discussed in the
Fermi catalog~\ref{first_cat,second_cat}. Furthermore, the galactic plane is
crowded and so it is often difficult to get a good model for the
region around a catalog source.  Because of this, finding a source with
$\tsext>16$ is not a sufficient test and we perform several crosschecks
to ensure our overall region is well modeled.

% 2FGL J1856.2+0450c = P72Y3047 for
As an example of why this issue, we describe our test of 
2FGL J1856.2+0450c for
extension.  Figure~\ref{example_bad_fit} shows a smoothed counts map
using photons with energy above 1 \gev. In the map, the galactic and isotropic diffuse
emission subtracted.  A two year catalog source 
2FGL J1856.2+0450c was found at the
position $(l,b)=(37.79\deg,1.14\deg)$.  
We find that there appears to be overall some large scale residual in the
diffuse emission along the galactic plane. Furthermore, it appears that
we don't have a great model of the nearby catalog sources. As a result,
2FGL J1856.2+0450c fits to a large extension of 1.37\deg and the result is
statistically significant with \tsext=51.6.  By looking at the residuals,
it is clear that this complicated region is not well fit even though
the source's extension is statistically significant. For this reason,
we have to perform a series of followup analysis for all of the sources
that are found with \tsext=16.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

Additionally,
we generated for each extended source candidate residual
test statistic (\ts) maps.  The residual \ts map is a map of the \ts
value evaluated at each point by adding onto the map at that position
a new source of spectral index 2 and finding the increase in likelihood
when fitting its flux. \ts maps are especially useful as looking for
new sources or other residual features that are not included in the
model. They also have the advantageous feature that the absolute scale
can be used to clearly look for when the residual is significant.
The downside is they are biased to look for residual features
that look like the PSF and so are not as sensitive to diffuse residual
features. Furthermore, since by definition \ts>0, \ts maps can only show
positive fluctuations. Nevertheless, \ts maps were useful for
assessing the overall quality of the fit. Figure~\ref{res_tsmap}
shows an example residual \ts map for the extended source IC443.

@@

@@

for sources that seemed promising, we performed in a case
by case basis a refit of the region where we would move or delete
background catalog sources until it was clear that we had obtained on
a case by case a good overal fit of the region. This was necessary in
many situations whrere the position of background sources in the catalog
was not consistent and when the offet of the background sources biased
the fit extension of our source. This was likey the case because the
catalog positions of the backgorund sources came usign all photons above
100 \mev and the low energy localization disagreed with the higher energy
localization we found. This also happened in certain situations because
the localization of a backgorund source dependend upon correctly modeling
the extended source as being extended and so once we fit our source for
extension, we had to relcoalizae the backgorund source.  For each source,
we descirbe in a case by case basis any modifications which were required
to obtain a good fit of our source and the surrounding region.

@@

To estimate systematic errors due to uncertaintly in our diffuse
emission background model, we performed an additional analysis
of our extended source candidates using an alternate diffuse
model. Our alterate model was based on the GALPROP\footnote{GALPROP
is a software package for calculating the dise Galactic $\gamma$-ray
emission based on a model of cosmic-ray propagation in the Galaxy. See
\url{http://galprop.stanford.edu/} for details and references} code
used in the LAT analysis of the isotropic diffuse emission
(\cite{isotropic_lat}).  In addition to using an alternate model, we
freeded additional compoents of this model and fit them simulatentously
with our source during the likelihood analysis. In particular,
we independently fit 7 HI rings, 7 HII rings, the inverse compoton,
and the E(B-V) residual component, and the isotropic and earth albedo
template. All told, there were 18 individual tempaltes where were all
simulatenously optimized during this analysis.

We do not expect that locally fitting tehse diffuse components would
produce a more physical model of the didffuse emission in the region.
But we do believe a source which does away when adding additional
degrees of freedom to the background model is likely spurious and so
this provides an important test of the valididity of our source.
The results of this fit for the new extended source candidates are
shown in table~\ref{alt_diff_model_results}. There is overal
good agreement between the \ts using the standard and alternate diffuse
models ($\ts_\gtlike$ and $\ts_\alt$ respectivly) and the \tsext values
(\tsextgtlike and \tsextalt respectivly).

\todo[inline]{Note about \ref{extension_profile}}

@@

We validated our method by testing for extension all of the sources
which the Fermi Collaboration had previously published on.  This list
includes the extended sources where were modeled in the two year catalog
(\cite{second_cat}).  This list contains the Large Magalenic Cloud
and the Small Magalenic Cloud which were previously published by the
LAT collaboration (\cite{lmc,smc}).  We also included the SNRs IC443, W28, W30, W44, W51C, and the Cygnus Loop which
were first published in \cite{ic443,w28,w30,w44,w51c,cygnus_loop}.
We include the Pulsar Wind Nebulae Vela X, MSH 15-52, and HESS
J1825-137\cite{velax,msh1552,fermi_hess_j1825}.  In addition to those
sources included by the catalog, we include in this list the SNR RX J1713.7-3946 which was recently published (\cite{RXJ1713}).

Since these sources are all included in the 2 year catalog, we applied
no special method to test these sources but used the same pipeline
that tested all other catalog sources for extension.  The results are
summarized in table~\ref{known_extended_sources}.  This table includes
the best fit position and extension. It also includes the source's
significance \ts and extension significance \tsext and the localization
error ellipse. The table also includes the best fit power-law spectral
model.

Using photons with energies greater than 1 \gev, our analysis succesfully
fit the extension of the LMC, SMC, IC443, W28, W30, W44, and W51C.
Using photons with energy above 10 \gev, we were able to succesffuly
fit the extesion of HESS J1825-137.
Our analysis of MSH 15-52 using photons with energy above 10 \gev found an extension
consistent with the publisehed result, but with $\tsext=11.2$. This is
most likely because the published analysis used a larger energy range,
considering all evnets above 6\gev. Looking at all photons with
energy above 1 \gev 
is problematic because of background source confusion whereas using photons
with energy above 10 \gev does not have the statistics for a significant dection.

Our analysis failed to detect the extension of Vela X. Vela X can only be
successfully analyzed after applying a phase cut to removed the heavily
dominant pular emission. It is beyond the scope of the paper to perform
such specialized analysis.

Our analysis also failed to detect a significant extension for the
Centaurus A Lobes.\cite{CenA paper}. This is most likely because the
discoverd emission was significantly more complicted then a uniform
radially symmetric Disk.  Furthermore, our analysis failed to correctly
fit the extension of the Cygnus Loop\cite{Cygnus Loop Paper}.  This is
most likely because Cygnus Loop is rather large and its shell type
morphology is not well represented by a uniform disk. The source is
also rather soft so the publisehd results used a larger energy range
then our search.

The difficulty our analysis analysis had fitting the extension of several
of the already published extended sources should be used to emphasize the
overal difficultly in studying spatially extendee sources with the Fermi
LAT, especially in the crowded galactic plane. For particular sources,
it is often necessary to perform careful and specalized analysis to
correctly find and model the sources we see. We can not claim our method
is complete.

@@

The final effect that could cause this discrepancy is an imperfect
modeling of the PSF.  Before launch, the PSF
was determined by a Monte Carlo simulation of the detector.
After launch, a discrepancy was found using flight data above a
few \gev in the PSF measured using bright AGN.  This result
was presented in conference and a publication is in preparation.
Subsequently, the PSF was fit empirically to bright AGN and this
empirical parameterization was used in our instrument
response function.
%\footnote{
%LAT Collaboraiton publication pending.
%https://confluence.slac.stanford.edu/download/attachments/102860834/FermiSymp2011_CAPSF_v5_ROTH.pptx
%}. 
But our current parameterization is not perfect. There are lingering
issues due to a lack of statistics at high energy which makes it hard to
validate the PSF as a function of the incident angle of the photon. Since
the distribution of incident angles varies from source to source, an
average PSF may make some of the sources look more and less extended
than the PSF.

@@

% Notes about extended Catalog sources
% Catalog used for analysis is P72Y_uw23.fits
% Compare to final catalog gll_psc_v04.fit
%          1FGL Name - Preliminary 2FGL - 2FGL Name
% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
% 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 
% 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138
% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
% N/A                - P72Y1287         - 2FGL J0851.7-4635

Eight new extended sources not included in the two year catalog
were found using this search. Three were found in our search using
events above 1 \gev and five were found in the search using events
above 10 \gev.  For all the extended sources, the results of our
fit are summarized in table~\ref{new_ext_srcs_table}. The table
includes for each source the best fit position, extension, spectrum,
source significance, and significance of extension.

@@

To get a good fit of the region we had to remove the nearby catalog
sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which are part of the
extended emission.  We tested the source for source confusion by fitting
it as two point sources. Because $\tsinc=21.9$ is smaller then \tsext,
we conclude that this is an extended source.  The removed catalog sources
are shown in figure~\ref{1FGL_J0823.3-4248}.

@@

\todo[inline]{Give some additional interpretation of the Puppis A SNR.}

@@

The two year catalog source 2FGL J1627.0-2425c was found to be
significantly extended when using photons with energies between 1 \gev
and 100 \gev.  The best fit extension was $0.53\deg\pm0.06\deg$ and the
best fit position is $(l,b)=(352.87\deg, 16.79\deg)$ The source also
appeared in the first LAT catalog as 1FGL J1628.6-2419c.  The extension
significance was $\tsext=20.3$.  A counts map showing this source is
seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
we also fit the source instead as two point sources. Since $\tsinc=19.3$
is smaller than \tsext, we conclude that this is an extended source.

@@

\todo[inline]{Can we get another citation about dark gas and stuff?
Better note about spectral index being typical of difuse emission.
Also does this description make sense?}

@@

The two year catalog source 2FGL J1554.4-5317c was found to be extended
using photons with energies between 1 \gev and 100 \gev.  We found an
extension of $0.52\deg\pm 0.04\deg$ and an extension significance of
$\tsext=37.6$ at a position $(l,b)=(328.12\deg,0.26\deg)$.  Figure
\ref{1FGL_J1554.0-5345c} shows a counts map of this source.
This source was found in the one year catalog with the name 1FGL J1554.0-5345c.

@@

\todo[inline]{
Add a better interpreation.
Explain that Vela Jr will be described better in upcoming publication???
}

>>>>

\begin{abstract}
We present a new method for analyzing spatially extended sources with
the Large Area Telescope (LAT), the primary science instrument
on the {\em Fermi Gamma-ray Space Telescope (Fermi)}.  We provide a
series of Monte Carlo studies to validate this tool
and calculate the LAT's detection threshold to spatially extended
sources.  We then apply this tool to test all sources in the two
year source catalog for extension. We present on the detection of
ten spatially extended sources in addition to the twelve spatially
extended sources reported in the second Fermi LAT Catalog.
\end{abstract}

\listoftodos

@@

@@

Being able to spatially resolve the \gev emission from a source is
important for several reasons. Because of the large point spread
function (PSF), there are often several possible source counterparts.
Finding a matching morphology can be used to uniquely identify the source.
Because of the largely varying PSF of the LAT, the spatial and spectral
information about a source do not nicely decouple. Therefore, a biased
spatial model will bias the spectral model of the source and studying
the extension of the source can correct for this.  Furthermore, correctly
modeling a source's extension is important for improving the overall model
of the sky and removing excess residuals.  These residuals manifested
themselves in the one year catalog as spurious point sources in the
region region surrounding the Large Magellanic Cloud (\cite{first_cat}).

@@

\pointlike is important for LAT analysis
that require many iterations such as source localization and extension
fitting.  On the other hand, we expect that the spectral parameters
fit by \gtlike to be slightly more precise.
Furthermore, because \gtlike is the standard likelihood analysis package,
it has been more extensively validated for spectral analysis.
For that reason, in the following analysis we took the best fit
position and extension found by \pointlike and
refit the spectral spectral parameters using \gtlike.
\gtlike also provides a second calculation of the likelihood which gives a
second measure of \ts and \tsext. We do not consider a source to be
significant unless there is agreement between the two methods.

@@

This is important when comparing morphologies to other wavelengths
because the quoted size can vary significantly depending on which quantity
is reported.  This effect can be best seen in figure~\ref{compare_r68}
which a counts map of an extended source simulated in the energy
range from 1 \gev to 100 \gev with a uniform disk spatial model and
$\sigma=05$. Overlaid on the plot is the fit extension assuming the
source has a uniform disk and a Gaussian spatial model. The plot overlays
both $\sigma$ and $\rsixeight$ and $\sigma$ is significantly larger for
the disk spatial hypothesis compared to the Gaussian spatial model. On
the other hand, the disk and Gaussian's 68\% containment radius are
similar.

@@

We simulated point sources of varying spectral models and fit them
them using \pointlike as both point and extended sources. The data was
simulated using \gtobssim\footnote{\gtobssim is distributed
by the Fermi Science Support Center (\cite{fssc}).}
The point sources were simulated with a power-law spectral model with
six $>100$ \mev fluxes ranging from $3\times 10^{-9} \ph/\cm^2/\sec$ to
$10^{-6} \ph/\cm^2/\sec$.  The point sources were simulated with spectral
indices ($\gamma$) of 1.5, 2, 2.5, and 3.  These values were picked to
to represent the types of sources detectable by the LAT.  The point
sources were simulated on top of an isotropic power-law background
with a Sreekumar-like spectrum ($>100$ \mev flux of 1.5e-5 and spectral
index 2.1) (\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
performed over a one year time interval using a default rocking profile
and a representative livetime fraction of 0.8.  The reconstruction was
performed with photons from an energy range of 1 \gev to 100 \gev using 4
energy bins per decade and using the 
Pass 7\_V6 (P7\_V6) Source Instrument
Response Function (IRFs).  For each point source, we used \pointlike
to fit it as both a point and extended source and calculate \tsext and
we only dept the sources which had a significant point source detection
($\ts>25$).

@@

The first and second LAT catalog produced a list of all significant point
sources seen by the LAT.  (\cite{first_cat,second_cat}).  The first LAT
catalog's source finding method assumes that all sources were consistent
with the PSF. The second LAT catalog modeled previously published
spatially extended sources with an extended spatial model but did not
attempt to resolve new spatially extended sources. In this paper,
we took the sources from the second Fermi LAT catalog and perform
a search to attempt to spatially resolve new sources.

For this search, we build a model of the
sky consistent with the second catalog.   We used the same two
years of data from August 4, 2008 to August 1, 2010 and we used the same
Pass 7\_V6 (P7\_V6) Source class event selections and 
Instrument Response Functions (IRFs, \cite{lat_on_orbit_psf}).  We used the same galactic diffuse,
isotropic diffuse, and earth limb emission model. The spectrum of the
galactic and isotropic diffuse models were refit during the analysis
while the earth limb emission was fixed to it's predicted value.

As was shown, we gain little in sensitivity using photons with energies
below 1 \gev. On the other hand, the large PSF at low energy makes us
more susceptible to systematic errors arising from source confusion due
to multiple point sources and susceptible to incorrect modeling of the
galactic diffuse emission.  For that reason, we performed our search
using photons only between 1 \gev and 100 \gev.
We used 4 energy bins per each logarithmic decade in energy.

We also performed a search for extended sources using photons only between
10 \gev and 100 \gev. Even though we are testing the same sources, this
approach is complimentary because there are regions in the galactic
plane where at lower energies the diffuse emission dominates and the
analysis is challenged by the difficulty in modeling this emission.
The analysis is also challenged by source confusion in crowded regions.
On the other hand, at the highest energies accessible by the LAT, the
galactic diffuse emission is less dominant and nearby sources might
be expected to be softer.  Using higher energies, we might expect
to detect harder sources in more complicated regions. This approach
is This is especially beneficial for regions near pulsars which
cutoff before 10 \gev.  This approach of using high energies was was
successfully used to detecting HESS J1825-137 and MSH 15-52 with the LAT
(\cite{msh1552,fermi_hess_j1825}).

For each catalog source, we tested it for extension using \pointlike
assuming the source had a uniform radially symmetric disk spatial model.
we used a circular $10\deg$ region of interest centered on our source and
included all catalog sources within $15\deg$ of the source of interest.
We refit the spectral parameters of sources within $2\deg$ of our source.
We modified the spectral index of each source we were testing to be a
power-law. This was reasonable because for a source to be significantly
extended, it would have to be fairly hard and fit reasonably well by
a power-law. Second, since we began our analysis at either 1 \gev or
10 \gev, we didn't expect there to be significant curvature over this
smaller energy range.

Finally, when analyzing our region, we automatically removed other
catalog sources which were within 0.5\deg of the source of interest. This was done because of
a concern that extended sources would end up in the catalog as
multiple point sources. These spurious catalogs sources would then
distort the extension fit.
For each extended candidate, we performed a dual localization procedure
(described in section~\ref{dual_localization_method} to test if the
source was extended multiple point sources.

@@

We then selected all of the
sources for which \pointlike found $\tsext>16$.

We expect most extended sources to be inside the galactic plane
since extragalactic sources are typically too far away to be
resolvable. Unfortunately, the \gev emission in the galactic plane
is dominated by anisotropic galactic diffuse emission.  Modeling the
galactic diffuse emission and finding sources on top of this emission is
difficult (\cite{first_diffuse_paper}). This issue has been discussed in the
Fermi catalog (\cite{first_cat,second_cat}). Furthermore, the galactic plane is
crowded and so it is often difficult to get a good model for the
region around a catalog source.  Because of this, finding a source with
$\tsext>16$ is not a sufficient test and we perform several crosschecks
to ensure our overall region is well modeled.

% 2FGL J1856.2+0450c = P72Y3047 for
As an example of why this issue, we describe our test of 2FGL
J1856.2+0450c for extension.  Figure~\ref{example_bad_fit} shows
a smoothed counts map using photons with energy above 1 \gev. In
the map, the galactic and isotropic diffuse emission subtracted.
A two year catalog source 2FGL J1856.2+0450c was found at the position
$(l,b)=(37.79\deg,1.14\deg)$.  We find that there appears to be overall
some large scale residual in the diffuse emission along the galactic
plane. Furthermore, it appears that we don't have a great model of
the nearby catalog sources. As a result, 2FGL J1856.2+0450c fits to a
large extension of 1.37\deg and the result is statistically significant
with \tsext=51.6.  By looking at the residuals, it is clear that this
complicated region is not well fit even though the source's extension is
statistically significant. For this reason, we have to perform a series
of further analysis for all of the sources that are found with \tsext=16.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

Additionally, we generated for each extended source candidate residual
test statistic (\ts) maps.  The residual \ts map is a map of the \ts
value evaluated at each point by adding onto the map at that position a
new source of spectral index 2 and finding the increase in likelihood
when fitting its flux. \ts maps are especially useful as looking for
new sources or other residual features that are not included in the
model. They also have the advantageous feature that the absolute scale
can be used to clearly look for when the residual is significant.
The downside is they are biased to look for residual features that
look like the PSF and so are not as sensitive to diffuse residual
features. Furthermore, since by definition \ts>0, \ts maps can only show
positive fluctuations. Nevertheless, \ts maps were useful for assessing
the overall quality of the fit. Figure~\ref{res_tsmaps} shows an example
residual \ts map for the extended source IC443.

@@

For each source, we computed an extension profile.  An example
extension profile for the extended source IC443 is shown in
figure~\ref{extension_profile}.

@@

Because of the high source density in the galactic plane for promising
extended source candidates we often had to iteratively improve our model
of background sources to obtain a good fit of the extended source.
Often, several catalog sources would fill in the emission of one
extended source and all but one of them would have to be removed from
the model. Similarly, the position of background sources would often
have to be refit once the extended source's extension was correctly
fit. Similarly, background sources were insignificant in the fit energy
range and had to be removed.  When the localization of background
sources and the extension of our catalog source coupled, we iteratively
fit the position and extended of the nearby sources in the region until
the fitter stabilized on the overall best fit positions and extensions.
For each extended source, we describe what modifications were required
to the sky model to obtain a good fit of the region.

@@

To estimate systematic errors due to uncertainty in our diffuse
emission background model, we performed a second
extension test of our candidates using
an alternate diffuse
model. Our alternate model was based on the GALPROP\footnote{GALPROP
is a software package for calculating the Galactic $\gamma$-ray
emission based on a model of cosmic-ray propagation in the Galaxy. See
\url{http://galprop.stanford.edu/} for details and references} code
used in the LAT analysis of the isotropic diffuse emission
(\cite{isotropic_lat}).  
With this model,
we independently fit in the nearby region 
7 HI rings, 7 HII rings, the inverse component,
the E(B-V) residual, and the isotropic component of
the background ration.
All told, we fit in or region 18 individual templates along
with all source parameters during the analysis.

It is not expected that this diffuse model is more physical.
But adding degrees of freedom to the background model is a good
way to remove additional degrees of freedom to the background
model is likely spurious sources which correlate to features in
the diffuse emission.  Therefore, this tests systematics that may
be due to incorrect modeling of the diffuse emission in the region.
The results of this fit for the new extended source candidates are shown
in table~\ref{alt_diff_model_results}. Overall, there is good agreement
between the \ts using the standard and alternate diffuse models.

@@

We first present on our analysis of the twelve extended sources
previously published and include in the second catalog's sky model.
(\cite{second_cat}).

% 6 SNRs
The largest population of extended source are SNRs. The six extended SNRs
included in the catalog are IC443, W28, W30, W44, W51C, and the Cygnus
Loop. These sources were first reported in (\cite{ic443,w28,w44,w51c}).
Detailed papers reporting on W30 and the Cygnus Loop are still in
preparation.  Using photons with energies greater than 1 \gev, our
analysis significantly detected the extension of the SNRs IC443, W28,
W30, W44, and W51C.

Our analysis failed to correctly fit the extension of the Cygnus Loop.
Publications describing the detailed analysis for the Cygnus Loop are
still in preparation.  This is most likely because Cygnus Loop is rather
large and its shell type morphology is not well represented by a uniform
disk. The source is also rather soft so the published results used a
larger energy range then our search.

% 2 galaxies

Two galaxies the Large Magalenic Cloud and the Small Magalenic Cloud 
were included in the second catalog (\cite{lmc,smc}).

% 3 PWN
Three pulsar wind nebula Vela X, MSH 15-52, and HESS J1825-137 
were included in the second catalog (\cite{velax,msh1552,fermi_hess_j1825}).

Our analysis failed to detect the extension of Vela X. Vela X can only be
successfully analyzed after applying a phase cut to removed the heavily
dominant pulsar emission. It is beyond the scope of the paper to perform
such specialized analysis.

Using photons with energy above 10 \gev, we significantly detected
the extension of HESS J1825-137.
Our analysis of MSH 15-52 using photons with energy above 10 \gev found an extension
consistent with the published result, but with $\tsext=11.2$. This is
most likely because the published analysis used a larger energy range,
considering all events above 6 \gev. Looking at all photons with
energy above 1 \gev 
is problematic because of background source confusion whereas using photons
with energy above 10 \gev does not have the statistics for a significant detection.

\todo[inline]{note about how MSH 15-52 and Vela X were hard
to analysze without phase cuts.}

% 1 radio galaxy
Centarus A.

Our analysis also failed to detect a significant extension for the
Centaurus A Lobes (\cite{cen_a_lat}). This is most likely because the
discovered emission was significantly more complicated then a uniform
radially symmetric Disk.

The results are summarized in table~\ref{known_extended_sources}.
This table includes the best fit position and extension of these
sources when fitting them with a radially symmetric uniform disk spatial
model.  It also includes the best fit spectral model of each source.
The difficulty our analysis analysis had fitting the extension of several
of the already published extended sources should be used to emphasize
the overall difficultly in studying spatially extended sources in crowded
regions of the sky.

@@

The final effect that could cause this discrepancy is an imperfect
modeling of the PSF.  Before launch, the PSF
was determined by a Monte Carlo simulation of the detector.
After launch, a discrepancy was found using flight data above a
few \gev in the PSF measured using bright AGN.  This result
was presented in conference and a publication is in preparation.
Subsequently, the PSF was fit empirically to bright AGN and this
empirical parameterization was used in our instrument
response function (\cite{lat_on_orbit_psf}).
But our current parameterization is not perfect. There are lingering
issues due to a lack of statistics at high energy which makes it hard to
validate the PSF as a function of the incident angle of the photon. Since
the distribution of incident angles varies from source to source, an
average PSF may make some of the sources look more and less extended
than the PSF.

@@

% Notes about extended Catalog sources
% Catalog used for analysis is P72Y_uw23.fits
% Compare to final catalog gll_psc_v04.fit
%          1FGL Name - Preliminary 2FGL - 2FGL Name
% 1FGL J1628.6-2419c - P72Y2516         - 2FGL J1627.0-2425c
% 1FGL J1554.0-5345c - P72Y2405         - 2FGL J1554.4-5317c
% 1FGL J0823.3-4248  - P72Y1212         - 2FGL J0823.0-4246
% 1FGL J1613.6-5100c - P72Y2472         - 2FGL J1615.0-5051 
% 1FGL J1614.7-5138c - P72Y2473         - 2FGL J1615.2-5138
% 1FGL J1632.9-4802c - P72Y2540         - 2FGL J1632.4-4753c
% 1FGL J1711.7-3944c - P72Y2674         - 2FGL J1712.4-3941
% 1FGL J2020.0+4049  - P72Y3281         - 2FGL J2021.5+4026
% 1FGL J1837.5-0659c - P72Y2974         - 2FGL J1837.3-0700c
% N/A                - P72Y1287         - 2FGL J0851.7-4635

Ten extended sources not include in the second LAT catalog were found
using this search.  Four were found in our search using only photons
with energies above 1 \gev and six were found only using photones with
energies above 10 \gev.  The fit properties of these ten sources is
summarized in table~\ref{new_ext_srcs_table}.  The table includes for each
source the best fit position, extension, spectrum, source significance,
and significance of extension.  Figure~\ref{allsky_extended_sources}
shows a skymap of the position of the twelve sources included in the
second catalog and the ten sources analysis in this paper.

@@

To get a good fit of the source, we had to remove the nearby catalog
sources 2FGL J0823.4-4305 and 2FGL J0821.0-4254 which are part of the
extended emission.  We tested the source for source confusion by fitting
it as two point sources. Because $\tsinc=21.9$ is smaller then \tsext,
we conclude that this is an extended source.  
These modifications are shown in
figure~\ref{1FGL_J0823.3-4248}.

@@

\todo[inline]{Add interpretations of Puppis A}

@@

The two year catalog source 2FGL J1627.0-2425c was found to be
significantly extended when using photons with energies between 1 \gev
and 100 \gev.  The best fit extension was $0.53\deg\pm0.06\deg$ and the
best fit position is $(l,b)=(352.87\deg, 16.79\deg)$.
The extension significance was $\tsext=20.3$. 
This source is coincident with the one year catalog source 1FGL J1628.6-2419c.
A counts map showing this source is
seen in figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
we also fit the source instead as two point sources. Since $\tsinc=19.3$
is smaller than \tsext, we conclude that this is an extended source.

@@

\todo[inline]{Can we get another citation about dark gas and stuff?
And a better description of spectral index being typical of diffuse emission.}

@@

The two year catalog source 2FGL J1554.4-5317c was found to be extended
using photons with energies between 1 \gev and 100 \gev.  We found an
extension of $0.52\deg\pm 0.04\deg$ and an extension significance of
$\tsext=37.6$ at a position $(l,b)=(328.12\deg,0.26\deg)$.  
This source is coincident with the one year catalog source 1FGL J1554.0-5345c.
Figure \ref{1FGL_J1554.0-5345c} shows a counts map of this source.

@@

\todo[inline]{Add interpretations of Vela Jr.. How to sync with upcoming publication?}
